\revision{Confirmation of \srcfull{} as a long period radio transient}{A new long period radio transient: Discovery of pulses repeating every 1.16 hours from \srcfull{}}

### 2025-07-15 paper/main.tex
Deleted now-redundant footnote

We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in \citetalias{2024MNRAS.535..909D}, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788. We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data. The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}.

>>>>

We also re-imaged the original 2023-05-28 L-band MeerKAT observation described in \citetalias{2024MNRAS.535..909D}, which was taken under project code DDT-20230525-DD-01 under capture block 1685306788. We performed a similar processing of the data, and identified four pulses with ToAs consistent with an ephemeris derived from the other data. The folded and stacked dynamic spectra are shown in \Fig~\ref{fig:stacked_spectra}.
%\footnote{The signal-to-noise of the MeerKAT detections was insufficient to improve on the localisation derived in \citetalias{2024MNRAS.535..909D}.}
